Hochschild cohomology of torus equivariant D-modules

### 2018-08-02 paper.tex
Potential confusions about the contraction principle.

Let $\stack X$ be a QCA stack with an action of $\Gm$.
We call the action \emph{(globally) contractive} if it can be extended to an action of the monoid $\as 1$.
Following the convention of \cite[Appendix~C]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG} we denote by $\stack X^0$ the stack of $\{0,1\}$-equivariant maps $\{0\} \to \stack X$.
The map $\{0\} \to \{0,1\}$ induces a \emph{contraction morphism} $\pi\colon \stack X \to \stack X^0$.

@@

\begin{remark}
  For our intended application in the proof of Theorem~\ref{thm:torus_quotient}, the special case of this statement for $\Gm$-quotient stacks is sufficient.
  In this case the statement can be proved directly without having to show the full \enquote{stacky} version, cf.~\cite[Proposition~5.3.2]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG}.
\end{remark}

>>>>

Let $\stack X$ be a QCA stack with an action of $\Gm$.
We call the action \emph{(globally) contractive} if it can be extended to an action of the monoid $\as 1$.
In this case we have in particular an action of the monoid $\{0,1\} \subset \as 1$ on $\stack X$.
Following the convention of \cite[Appendix~C]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG} we denote by $\stack X^0$ the stack of $\{0,1\}$-equivariant maps $\{0\} \to \stack X$.
The map $\{0\} \to \{0,1\}$ induces a \emph{contraction morphism} $\pi\colon \stack X \to \stack X^0$, while the map $\{0,1\} \to \{0\}$ induces an inclusion morphism $i\colon \stack X^0 \hookrightarrow \stack X$.

@@

\begin{remark}
    At first glance the requirement that the $\Gm$-action is trivial may seems paradoxical.
    The example that the reader should keep in mind is the stack $\stack X = \as1/\Gm$, where the quotient is taken via the usual action of $\Gm$.
    There is an action of $\Gm$ on $\stack X$ which comes from the action of $\Gm$ on $\as 1$.
    This action is clearly trivial.
    On the other hand it can be extended to an action of $\as 1$, again induced from the action on the cover.
    This action is not trivial and is the one that defines $\stack X^0 = \cs{\Gm}$.
\end{remark}

\begin{remark}
  For our intended application in the proof of Theorem~\ref{thm:torus_quotient}, the special case of this statement for $\Gm$-quotient stacks is sufficient.
  In this case the statement can be proved directly without having to show the full \enquote{stacky} version, cf.~\cite[Proposition~5.3.2]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG}.
  We have elected to state the theorem as above in order to have a general version of the following proposition for future applications.
\end{remark}
